Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean (*Phaseolus vulgaris*) in the United States

### 2017-11-02 doc/manuscript/manuscript.Rmd
add more footnotes to Supplementary Info to address #15

The number of observed alleles per locus ranged from two to 10 with an average of `r signif(Amean, 3)` (Table \@ref(tab:locus-stats)).
Locus `r loc_table$Locus[loc_table$allele==2]`, which contained only 2 alleles, showed low values of both *h* (`r signif(loc_table$Hexp[loc_table$allele==2], 3)`) and evenness (`r signif(loc_table$Evenness[loc_table$allele==2], 3)`), indicating that there was one dominant allele present. 
Analysis of the haplotype accumulation curve showed no clear plateau for 11 or 16 loci (Supplemental Information), indicating that we would likely obtain more multilocus haplotypes if we were to genotype more loci.

@@

The analysis of molecular variance (AMOVA) for clone-corrected samples over the hierarchy of Region, Source, and Year showed significant variation between Regions and Years, but no significant variation between wmn and producer fields (Table \@ref(tab:amova)).
In contrast, when we compared the three cultivars, Beryl, Bunsi, and G122, we found no significant differentiation (Supplementary Information).

>>>>

The number of observed alleles per locus ranged from two to 10 with an average of `r signif(Amean, 3)` (Table \@ref(tab:locus-stats)).
Locus `r loc_table$Locus[loc_table$allele==2]`, which contained only 2 alleles, showed low values of both *h* (`r signif(loc_table$Hexp[loc_table$allele==2], 3)`) and evenness (`r signif(loc_table$Evenness[loc_table$allele==2], 3)`), indicating that there was one dominant allele present. 
Analysis of the haplotype accumulation curve showed no clear plateau for 11 or 16 loci (Supplementary Information[^1]), indicating that we would likely obtain more multilocus haplotypes if we were to genotype more loci.

[^1]: https://github.com/everhartlab/sclerotinia-366/blob/v1.0/results/MLG-distribution.md#loading-data-and-setting-strata

@@

The analysis of molecular variance (AMOVA) for clone-corrected samples over the hierarchy of Region, Source, and Year showed significant variation between Regions and Years, but no significant variation between wmn and producer fields (Table \@ref(tab:amova)).
In contrast, when we compared the three cultivars, Beryl, Bunsi, and G122, we found no significant differentiation (Supplementary Information[^2]).

[^2]: https://github.com/everhartlab/sclerotinia-366/blob/v1.0/results/wmn-differentiation.md#host-differentiation
